Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-03-08 paper/current/main.tex
Plot times ranking vs. leiden ranking correlation

In addition to learning geography, its clear that the \SGNS{} model is also encoding the latent prestige hierarchies of academic mobility.
To test this, we derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings.
SemRank is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
We find that SemRank derived is highly correlated with the Times ranking ($\rho = 0.81$, Fig.~\ref{fig:semaxis}b).
This correlation is robust with the number of organizations used to define the axes (Fig. SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking ($\rho = 0.46$).
For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking mean-normalized citation score ($\rho = 0.87$).
This suggests that \SGNS{} model, in addition to learning the latent geography of mobility, while capture more nuanced characteristics such as latent hierarchy in the axis of the embedding, which is fascinating characteristic of our approach.

@@

>>>>

In addition to learning geography, its clear that the \SGNS{} model is also encoding the latent prestige hierarchies of academic mobility.
To test this, we derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings.
SemRank is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
We find that SemRank derived is highly correlated with the Times ranking ($\rho = 0.81$, Fig.~\ref{fig:semaxis}b).
This correlation is robust with the number of organizations used to define the axes (Fig. SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking ($\rho = 0.46$).
For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking mean-normalized citation score ($\rho = 0.87$, Fig.~\ref{fig:supp:times_vs_leiden}).
This suggests that \SGNS{} model, in addition to learning the latent geography of mobility, while capture more nuanced characteristics such as latent hierarchy in the axis of the embedding, which is fascinating characteristic of our approach.

@@

%
% Figure - Times Ranking vs. Leiden Ranking
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/times_leiden_compare.pdf}
	\caption{
		\textbf{Correlation between Times and Leiden Ranking.}
		Comparison between the Times and Leiden rankings of universities.
		Here, the Leiden Ranking is operationalized as the mean normalized fractional citation impact for each university~\autocite{waltman2012leidenrankings}. 
	  	PCC details the estimate from Spearman correlation between the two rankings.
	}
	\label{fig:supp:times_vs_leiden}
\end{figure}
